Hannah Yu

### 2024-01-23 outputs/paper/paper.qmd
deleted some files

---
title: "Hannah Yu"
author: 
  - Hannah Yu
thanks: "Code and data are available at: "
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

## Introduction

@@

The Police Annual Statistical Report - Homicides [@citehomicidedata] from [@ropendatatoronto] provides a record of all homicide cases in Toronto from 2004-2020 including the time of occurrence, location, and type of homicide. we could draw information about homicide cases and their related characteristics from this extensive dataset, and investigate Toronto’s homicide patterns across time. In Section 2, I introduce the dataset and some general information. In Section 2.1 ## General Homicide Analysis, I navigate the change in homicide case numbers across time with various characteristics and perform some analysis on the relationship between homicide cases and time variables. And in Section 2.2, I redo most of the analysis on the top five neighborhood with the most amount of homicide cases. Lastly, I discuss the implications and further discussions on these results in Section 3.

The remainder of this paper is structured as follows. @sec-data....

## Data {#sec-data}

To investigate the homicide cases in Toronto, I obtained the dataset “ Police Annual Statistical Report - Homicides [@citehomicidedata] from the Toronto Open Data Portal [@ropendatatoronto]. Data was cleaned and analyzed using the open source statistical programming language R [@citer], with additional support from 'tidyverse' [@rtidyverse], 'dplyr' [@rdplyr], 'janitor'[@rjanitor], 'readr' [@rreadr] , 'stringr' [@rstringr], 'lubridate' [@rlubridate], 'ggplot2' [@rggplot2], 'kableExtra' [@rkableExtra], ''  Further details about data extraction and analyzation processes will be discussed in the following sections below.

@@

```
## General Homicide Analysis

@@

```
## Homicide Analysis in Top Five Neighborhood

@@

## Discussion

>>>>

---
title: "Hannah Yu"
author: 
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/Toronto-Homicide-Analysis"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Introduction

@@

The Police Annual Statistical Report - Homicides [@citehomicidedata] from [@ropendatatoronto] provides a record of all homicide cases in Toronto from 2004-2020 including the time of occurrence, location, and type of homicide. we could draw information about homicide cases and their related characteristics from this extensive dataset, and investigate Toronto’s homicide patterns across time. In @sec-data, I introduce the dataset and some general information. In @subsec1-data, I navigate the change in homicide case numbers across time with various characteristics and perform some analysis on the relationship between homicide cases and time variables. And in @subsec2-data, I redo most of the analysis on the top five neighborhood with the most amount of homicide cases. Lastly, I discuss the implications and further discussions on these results in @sec-discussion.

# Data {#sec-data}

To investigate the homicide cases in Toronto, I obtained the dataset “ Police Annual Statistical Report - Homicides [@citehomicidedata] from the Toronto Open Data Portal [@ropendatatoronto]. Data was cleaned and analyzed using the open source statistical programming language R [@citer], with additional support from 'tidyverse' [@rtidyverse], 'dplyr' [@rdplyr], 'janitor'[@rjanitor], 'readr' [@rreadr] , 'stringr' [@rstringr], 'lubridate' [@rlubridate], 'ggplot2' [@rggplot2], 'kableExtra' [@rkableExtra], 'gt'[@rgt]. Further details about data extraction and analyzation processes will be discussed in the following sections below.

@@

```
## General Homicide Analysis {#subsec1-data}

@@

```
## Homicide Analysis in Top Five Neighborhood {#subsec2-data}

@@

# Discussion {#sec-discussion}
